Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
space savings

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along
valid topological paths if the routing policy disallows it. 
\dpw{I deleted this:  ``It implies that we cannot use standard graph theoretic algorithms.''  I don't know of any ``standard'' graph-theoretic algorithm
we could use but I can't completely rule it out either because I don't
know all graph theoretic algorithms and it wouldn't completely shock 
me if somewhere there were algorithms for analyzing graphs modulo
isomorphisms that might be related tangentially.  Basically, I think
it brings up the possibility that we should compare with graph-theoretic
algorithms but then we don't do so in any detail
so I thought it was better to drop it.}

>>>>

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along
valid topological paths if the routing policy disallows it.
